---
title: "Appendix S2. Full fish consumption survey results"

output:
  output: pdf_document
toc: false
header-includes:
  - \usepackage{caption}
  - \DeclareCaptionLabelFormat{nospace}{#1-#2}
  - \captionsetup[figure]{labelformat=nospace}
  - \captionsetup[table]{labelformat=nospace}

---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
library(bookdown)
```

\def\figurename{Figure S2}
\def\tablename{Table S2}


```{r DataClean, include=FALSE}
library(tidyverse)
library(here)     # file paths
library(lubridate)
library(arm)
library(janitor) # frequency tables & crosstabs

options(scipen = 100)  # disabled scientific notation

##########################
## Data prep for analysis
##########################

## Delete rows 2 & 3 in downloaded data file before importing
mydata <- read_csv(
  here("data/raw_data/EPA_fish_consumption.csv"))
mydata <- dplyr::select(mydata, Q2:Q45)

# add an id number
mydata <- mydata %>%
  mutate(id = 1:n()) %>%
  relocate(id)

# convert character vectors to numeric
mydata <- mydata %>% mutate_if(is.character, as.numeric)

### filter data for eligible respondents - 
# 55 years of age or younger
mydata <- filter(mydata, Q43_1_TEXT < 56)
mydata <- filter(mydata, Q43_1_TEXT != -99)

# Potential respondents intercepted at food pantries
answers <- c("Yes", "No", "Don't know/Not sure", "Preferred not to answer")

coding <- function(x) {
  if_else(x==1, "Yes", if_else(x==2,"No", "Don't know/Not sure"))
}
mydata <- mydata %>%
  mutate_at(vars("Q2","Q4", "Q6"), list(factor=coding))

mydata <- mydata %>%  
  mutate(across(c(Q2_factor, Q4_factor, Q6_factor), ~factor(.x, levels=answers))) 

# Replace -99 with NA
mydata <- mydata %>%
  mutate(across(where(is.numeric), ~na_if(., -99)))

### generate new variables as factors ###
# tribal enrollment
tribal <- c("Salish", "Kootenai", "Pend d'Oreille","Other", "Don't know/Prefer not to answer")

mydata <- mydata %>%
  mutate(
    Q3_factor = case_when(
      Q2 == 1 & Q3 == 1 ~ "Salish",
      Q2 == 1 & Q3 == 2   ~ "Kootenai",
      Q2 == 1 & Q3 == 3  ~ "Pend d'Oreille",
      Q2 == 1 & Q3 == 4 ~ "Don't know/Prefer not to answer"),
    Q3_factor = factor(Q3_factor, levels = tribal)
  )

mydata <- mydata %>%
  mutate(
    Tribal.factor = case_when(
      Q2 == 1 & Q3 == 1 ~ "Salish",
      Q2 == 1 & Q3 == 2   ~ "Kootenai",
      Q2 == 1 & Q3 == 3  ~ "Pend d'Oreille",
      Q4 == 1 ~ "Other"),
    Tribal.factor = factor(Tribal.factor, levels = tribal)
    )
# fish meal levels - included "One or fewer" to mimic 2008 study category
# for those who replied yes to eating fish, but number of meals was recorded as zero, assumed "1 or fewer" meals per month
fish_meals <- c("Zero", "One meal or less", "2-4 meals", "5-8 meals", "9 or more")
mydata <- mydata %>%
  mutate(
    Meal.factor = case_when(
      is.na(Q13_1_TEXT) ~ "Zero",
      Q13_1_TEXT == 0 ~ "One meal or less",
      Q13_1_TEXT == 1 ~ "One meal or less",
      between(Q13_1_TEXT,2,4) ~ "2-4 meals",
      between(Q13_1_TEXT,5,8) ~ "5-8 meals",
      TRUE ~ "9 or more"),
    Meal.factor = factor(Meal.factor, levels = fish_meals)
    )

# Size of catch
catch_size <- c("Small (less than 14 in.)", "Medium (14 to 26 in.)", "Large (over 26 in.)", "Don't know/Not sure", "Preferred not to answer")
mydata <- mydata %>%
  mutate(
    Catch.factor = case_when(
      Q32 == 1 ~ "Small (less than 14 in.)",
      Q32 == 2 ~ "Medium (14 to 26 in.)",
      Q32 == 3 ~ "Large (over 26 in.)",
      Q32 == 4 ~ "Don't know/Not sure",
      Q32 == 5 ~ "Preferred not to answer"),
    Catch.factor = factor (Catch.factor, levels  = catch_size)
    )
# Knowledge of Hg contamination
Hg_know <- c("A lot", "Some", "Very little", "Nothing at all", "Don't know/Not sure", "Preferred not to answer")
mydata <- mydata %>%
  mutate(
    HgKnow.factor = case_when(
      Q34 == 1 ~ "A lot",
      Q34 == 2  ~ "Some",
      Q34 == 3 ~ "Very little",
      Q34 == 4 ~ "Nothing at all",
      Q34 == 5 ~ "Don't know/Not sure",
      Q34 == 6 ~ "Preferred not to answer"),
    HgKnow.factor = factor(HgKnow.factor, levels = Hg_know)
    )
# Knowledge of fish species
mydata <- mydata %>%
  mutate(
    Species.factor = case_when(
      Q38 == 1 ~ "A lot",
      Q38 == 2  ~ "Some",
      Q38 == 3 ~ "Very little",
      Q38 == 4 ~ "Nothing at all",
      Q38 == 5 ~ "Don't know/Not sure",
      Q38 == 6 ~ "Preferred not to answer"),
    Species.factor = factor(Species.factor, levels = Hg_know)
    )
# Knowledge of size restrictions
mydata <- mydata %>%
  mutate(
    Size.factor = case_when(
      Q39 == 1 ~ "A lot",
      Q39 == 2  ~ "Some",
      Q39 == 3 ~ "Very little",
      Q39 == 4 ~ "Nothing at all",
      Q39 == 5 ~ "Don't know/Not sure",
      Q39 == 6 ~ "Preferred not to answer"),
    Size.factor = factor(Size.factor, levels = Hg_know)
    )
# Knowledge of amount of fish one can eat
mydata <- mydata %>%
  mutate(
    Quantity.factor = case_when(
      Q40 == 1 ~ "A lot",
      Q40 == 2  ~ "Some",
      Q40 == 3 ~ "Very little",
      Q40 == 4 ~ "Nothing at all",
      Q40 == 5 ~ "Don't know/Not sure",
      Q40 == 6 ~ "Preferred not to answer"),
    Quantity.factor = factor(Quantity.factor, levels = Hg_know)
    )
# Visits to food pantry
visits <- c("Every month", "Every other month", "Once every 3 months", "Infrequently", "Don't know/Not sure", "Preferred not to answer")
mydata <- mydata %>%
  mutate(
    Visit.factor = case_when(
      Q42 == 1 ~ "Every month",
      Q42 == 2 ~ "Every other month",
      Q42 == 3 ~ "Once every 3 months",
      Q42 == 4 ~ "Infrequently",
      Q42 == 5 ~ "Don't know/Not sure",
      Q42 == 6 ~ "Preferred not to answer"),
    Visit.factor = factor (Visit.factor, levels = visits)
    )
# Age categories
ages <- c("Under 18", "18-25", "26-35", "36-45", "46-55", "55+", "Preferred not to answer")
mydata <- mydata %>%
  mutate(
    Age.factor = case_when(
      is.na(Q43_1_TEXT) ~ "Preferred not to answer",
      between(Q43_1_TEXT,0,17)  ~ "Under 18",
      between(Q43_1_TEXT,18,25) ~ "18-25",
      between(Q43_1_TEXT,26,35) ~ "26-35",
      between(Q43_1_TEXT,36,45) ~ "36-45",
      between(Q43_1_TEXT,46,55) ~ "46-55",
      TRUE ~ "55+"),
    Age.factor = factor(Age.factor, levels = ages)
  )
# Relationship categories
relation <- c("Single", "Married", "Member of an unmarried couple", "Divorced/Separated", "Don't know/Not sure", "Preferred not to answer")
mydata <- mydata %>%
  mutate(
    Relationship.factor = case_when(
      Q44 == 1 ~ "Single",
      Q44 == 2 ~ "Married",
      Q44 == 3 ~ "Member of an unmarried couple",
      Q44 == 4 ~ "Divorced/Separated",
      Q44 == 5 ~ "Don't know/Not sure",
      TRUE ~ "Preferred not to answer"),
    Relationship.factor = factor(Relationship.factor, levels = relation)
    )
# Education categories
education <- c("Less than high school", "High school or GED", "Associates degree", "Bachelors degree", "Graduate degree", "Don't know/Not sure", "Preferred not to answer")
mydata <- mydata %>%
  mutate(
    Education.factor = case_when(
      Q45 == 1 ~ "Less than high school",
      Q45 == 2 ~ "High school or GED",
      Q45 == 3 ~ "Associates degree",
      Q45 == 4 ~ "Bachelors degree",
      Q45 == 5 ~ "Graduate degree",
      Q45 == 6 ~ "Don't know/Not sure",
      TRUE ~ "Preferred not to answer"),
    Education.factor = factor(Education.factor, levels = education)
    )
# Yes, no and don't know questions
answers <- c("Yes", "No", "Don't know/Not sure", "Preferred not to answer")

coding <- function(x) {
  if_else(x==1, "Yes", if_else(x==2,"No", "Don't know/Not sure"))
}
mydata <- mydata %>%
  mutate_at(vars("Q14":"Q31", "Q35"), list(factor=coding))

mydata <- mydata %>%  
  mutate(across(c(Q14_factor:Q31_factor, Q35_factor), ~factor(.x, levels=answers))) 

# Eats fish
##fish_meals <- c("Zero", "Less than one", "One meal", "2-4 meals", "5-8 meals", "9 or more")
mydata <- mydata %>%
  mutate(Fish.eater = ifelse(`Meal.factor` == "Zero", 0, 1))

### Summary tables ###
# Enrolled member of CSKT  
Enrolled.CSKT.out <- mydata %>%
  count(Q2_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))

# Tribal identification among CSKT
Tribe.CSKT.out <- mydata %>%
  filter(!is.na(Q3_factor)) %>%
  count(Q3_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))

# Enrolled in any American Indian tribe
Enrolled.Other.out <- mydata %>%
  filter(!is.na(Q4_factor)) %>%
  count(Q4_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))

# Tribal affiliation -all- of surveyed individuals
Tribal.out <- mydata %>%
  filter(!is.na(Tribal.factor)) %>%
  count(Tribal.factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))

### filter data for eligible respondents - 
# enrolled in CSKT or other recognized tribe
mydata <- filter(mydata, Q9 == 1)

# Meal frequency in 2021 & 2008
Meal.out <- mydata %>%
  count(Meal.factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
Meal.out <- Meal.out %>%
  add_column(n.2008=c("--", 36, 23, 6), percent.2008=c("--", 55, 35, 10))%>%
  group_by(Meal.factor)

### Fish products bought at markets
# Shellfish
Market.Shellfish.out <- mydata %>%
  filter(!is.na(Q14_factor)) %>%
  count(Q14_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Fish fillets, fish sticks, or fish sandwiches
Market.Fillets.out <- mydata %>%
  filter(!is.na(Q16_factor)) %>%
  count(Q16_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Light tuna
Market.Tuna.out <- mydata %>%
  filter(!is.na(Q19_factor)) %>%
  count(Q19_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Albacore tuna
Market.Albacore.out <- mydata %>%
  filter(!is.na(Q20_factor)) %>%
  count(Q20_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
### Fish products received from the food pantry
# Shellfish
Pantry.Shellfish.out <- mydata %>%
  filter(!is.na(Q21_factor)) %>%
  count(Q21_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
Pantry.Fillets.out <- mydata %>%
  filter(!is.na(Q22_factor)) %>%
  count(Q22_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Light tuna
Pantry.Tuna.out <- mydata %>%
  filter(!is.na(Q24_factor)) %>%
  count(Q24_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Albacore tuna
Pantry.Albacore.out <- mydata %>%
  filter(!is.na(Q25_factor)) %>%
  count(Q25_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Ate fish donated to food pantry (Q26)
Donated.fish.out <- mydata %>%
  filter(!is.na(Q26_factor)) %>%
  count(Q26_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Ate donated Lake Trout (Q27)
Donated.lake.trout.out <- mydata %>%
  filter(!is.na(Q27_factor)) %>%
  count(Q27_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Ate donated whitefish (Q28)
Donated.whitefish.out <- mydata %>%
  filter(!is.na(Q28_factor)) %>%
  count(Q28_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Ate angler caught fish (Q29) + 2008 study results
Caught.fish.out <- mydata %>%
  filter(!is.na(Q29_factor)) %>%
  count(Q29_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
Caught.fish.out <- Caught.fish.out %>%
  rename(n.2021=n, percent.2021=percent)
Caught.fish.out <- Caught.fish.out %>%
  add_column(n.2008=c(33, 32), percent.2008=c(51, 49))%>%
  group_by(Q29_factor)
Caught.fish.out <- setNames(Caught.fish.out, c("Q29_factor","n", "percent", "n", "percent")) # rename columns in base R
# Ate angler caught lake trout (Q30)
Caught.lake.trout.out <- mydata %>%
  filter(!is.na(Q30_factor)) %>%
  count(Q30_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Ate angler caught whitefish (Q31)
Caught.whitefish.out <- mydata %>%
  filter(!is.na(Q31_factor)) %>%
  count(Q31_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Size of angler caught fish
Catch.Size.out <- mydata %>%
  filter(!is.na(Catch.factor)) %>%
  count(Catch.factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
### Knows about mercury contamination + 2008 study results
HgKnow.out <- mydata %>%
  count(HgKnow.factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
HgKnow.out <- HgKnow.out %>%
  rename(n.2021=n, percent.2021=percent)
HgKnow.out <- HgKnow.out %>%
  add_column(n.2008=c(1, 8, 28, 28, 0), percent.2008=c(2, 12, 43, 43, 0)) %>%  
  group_by(HgKnow.factor)
# rename columns in base R
HgKnow.out <- setNames(HgKnow.out, c("HgKnow.factor","n", "percent", "n", "percent")) 
### Awareness of CSKT's fish advisory (Q35) + 2008 study results
Advisory.out <- mydata %>%
  count(Q35_factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
Advisory.out <- Advisory.out %>%
  rename(n.2021=n, percent.2021=percent)
Advisory.out <- Advisory.out %>%
  add_column(n.2008=c(13, 52, 0), percent.2008=c(20, 80, 0))%>%
  group_by(Q35_factor)
# rename columns in base R
Advisory.out <- setNames(Advisory.out, c("Advisory.factor","n", "percent", "n", "percent")) 
### Source for learning about CSKT's fish advisory
Knew <- as.vector(Advisory.out[1,2])  # total number of recipients that knew of advisory

Advisory.source <- mydata %>% 
  summarise(across(Q36_1:Q36_9, \(x) sum(x, na.rm=TRUE))) %>% 
  t()  # rotates columns to rows
Advisory.source <- as.data.frame(Advisory.source) 
  
colnames(Advisory.source)[1] <- "Count"
rownames(Advisory.source) <- NULL

Advisory.source <- Advisory.source %>%
  dplyr::select(Count) %>% 
  mutate(Percent=round((Count/19*100), digits=0))

Advisory.source <- cbind(c("TV", "Radio", "Internet", "Brochures", "Mack Days", 
                           "Tribal government agencies", "Talking to doctors/health professional",
                           "Talking to people you know", "Signs or posters"), 
                           Advisory.source)
colnames(Advisory.source)[1] <- "Source"

### Knowledge of fish species + 2008 study results
Species.out <- mydata %>%
  filter(!is.na(Species.factor)) %>%
  count(Species.factor, .drop=FALSE) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
Species.out <- Species.out %>% 
  filter(!row_number() %in% c(5,6))
Species.out <- Species.out %>%
  rename(n.2021=n, percent.2021=percent)
Species.out <- Species.out %>%
  add_column(n.2008=c(0, 0, 6, 7), percent.2008=c(0, 0, 46, 54))%>%
  group_by(Species.factor)
# rename columns in base R
Species.out <- setNames(Species.out, c("Species.factor","n", "percent", "n", "percent")) 
### Knowledge of fish size
Size.out <- mydata %>%
  filter(!is.na(Size.factor)) %>%
  count(Size.factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
Size.out <- Size.out %>%
  rename(n.2021=n, percent.2021=percent)
Size.out <- Size.out %>%
  add_column(n.2008=c(0, 1, 5, 7), percent.2008=c(0, 8, 38, 54))%>%
  group_by(Size.factor)
# rename columns in base R
Size.out <- setNames(Size.out, c("Size.factor","n", "percent", "n", "percent")) 
### Knowledge of amount of fish
Quantity.out <- mydata %>%
  filter(!is.na(Quantity.factor)) %>%
  count(Quantity.factor) %>%
  mutate(percent=round((n/sum(n)*100), digits = 0))
Quantity.out <- Quantity.out %>%
  rename(n.2021=n, percent.2021=percent)
Quantity.out <- Quantity.out %>%
  add_column(n.2008=c(0, 0, 6, 7), percent.2008=c(0, 0, 46, 54))%>%
  group_by(Quantity.factor)
# rename columns in base R
Quantity.out <- setNames(Quantity.out, c("Quantity.factor","n", "percent", "n", "percent")) 

### Demographics
# Number of visits to the food pantry per month
Visits.out <- mydata %>% 
  count(Visit.factor) %>% 
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Age
Age.out <- mydata %>% 
  count(Age.factor) %>% 
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Relationship status
Relationship.out <- mydata %>% 
  count(Relationship.factor) %>% 
  mutate(percent=round((n/sum(n)*100), digits = 0))
# Education
Education.out <- mydata %>% 
  count(Education.factor) %>% 
  mutate(percent=round((n/sum(n)*100), digits = 0))
```
## Results of Food Pantry Survey

Summarized below are the results of surveys completed with female Tribal members of child-bearing age relying on assistance from food pantries.  The survey included questions that assess fish consumption and advisory awareness plus demographic questions.

## Screening for tribal enrollment

Q2. I have to ask, are you an enrolled member of the Confederated Salish and Kootenai Tribes? 
```{r Enrolled, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
knitr::kable(Enrolled.CSKT.out,
       booktabs = TRUE,
       col.names = c("Enrolled in CSKT","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Respondents enrolled in CSKT') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
  
```

Q3. Which Tribe in the Confederation do you identify with most closely?
```{r Tribes, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
knitr::kable(Tribe.CSKT.out,
       booktabs = TRUE,
       col.names = c("Tribe","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Respondents CSKT tribal affiliation') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
  
```

Q4. Are you enrolled in any American Indian tribe or Alaska Native tribe or village?
```{r Other tribe, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
knitr::kable(Enrolled.Other.out,
       booktabs = TRUE,
       col.names = c("Enrolled in any tribe","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Respondents enrolled in any American Indian tribe or Alaska Native tribe or village') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))

```
\newpage
```{r Eligible summary, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
knitr::kable(Tribal.out,
       booktabs = TRUE,
       col.names = c("Tribe","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Eligible responents by tribal affiliation') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```


## Fish Consumption
This first set of questions are about how much fish you eat in a typical month, the types of fish, and where the fish came from.

Q13. During the average month, about how many meals of fish do you eat including all types of freshwater and saltwater fish either purchased, received from a food pantry, or caught in local waters?

```{r Meals, echo=FALSE}
knitr::kable(Meal.out,
       booktabs = TRUE,
       col.names = c("Meals","n","%", "n", "%"), 
       align = c('l', rep('c', 4)),
       caption = 'Amount of fish consumed') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position")) %>% 
  add_header_above(c(" " = 1, "2021 study"= 2, "2008 study"= 2))

```

*The following questions were asked of those who said they eat at least one fish meal in an average month.*

Q14. Over the last 12 months, whate types of fish did you **purchase at a market or store**? Did you **purchase** shellfish such as shrimp, lobster, clams, crab, crayfish, or imitation shellfish?
```{r Market Shellfish, echo=FALSE}
knitr::kable(Market.Shellfish.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Purchased shellfish (shrimp, lobster, clams, crab, crayfish, or imitation shellfish') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```

Q16. Did you **purchase** fish fillets, fish sticks, or fish sandwiches?
```{r Market Fillets, echo=FALSE}
knitr::kable(Market.Fillets.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Purchased fish fillets, fish sticks, or fish sandwiches') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```
\newpage
Q18. Did you **purchase** either light tuna or albacore tuna?

Q19. Light tuna
```{r Market Tuna, echo=FALSE}
knitr::kable(Market.Tuna.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Purchased light tuna') %>%
  kable_styling(full_width=FALSE, latex_options=c("HOLD_position"))
```

Q20. Albacore tuna
```{r Market Albacore, echo=FALSE}
knitr::kable(Market.Albacore.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Purchased albacore tuna') %>%
  kable_styling(full_width=FALSE, latex_options=c("HOLD_position"))
```

Q21. Over the last 12 months, what types of fish did you **receive from the food pantry**? Did you **receive** shellfish such as shrimp, lobster, clams, crab, crayfish, or imitation shellfish?
```{r Pantry Shellfish, echo=FALSE}
knitr::kable(Pantry.Shellfish.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Food pantry supplied shellfish (shrimp, lobster, clams, crab, crayfish, or imitation shellfish') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))

```

Q22. Did you **receive** fish fillets, fish sticks, or fish sandwiches?
```{r Pantry Fillets, echo=FALSE}
knitr::kable(Pantry.Fillets.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Food pantry supplied fish fillets, fish sticks, or fish sandwiches') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```

Q23. Did you **receive** either light tuna or albacore tuna?

Q24. Light tuna
```{r Pantry Tuna, echo=FALSE}
knitr::kable(Pantry.Tuna.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Food pantry supplied light tuna') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```
\newpage
Q25. Albacore tuna
```{r Pantry Albacore, echo=FALSE}
knitr::kable(Pantry.Albacore.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Food pantry supplied albacore tuna') %>%
  kable_styling(full_width=FALSE, latex_options=c("HOLD_position"))
```

Q26. Do you or your family ever eat fish fillets **donated** to this food pantry by the Tribes?
```{r Donated fish, echo=FALSE}
knitr::kable(Donated.fish.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Ate fish fillets donated by the Tribes') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```

Q27. When you eat tribally **donated** fish fillets, which types of fish do you normally eat? Do you eat lake trout?
```{r Donated Lake Trout, echo=FALSE}
knitr::kable(Donated.lake.trout.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Ate donated lake trout fillets') %>%
  kable_styling(full_width=FALSE, latex_options=c("HOLD_position"))
```

Q28. Do you eat lake whitefish?
```{r Donated Whitefish, echo=FALSE}
knitr::kable(Donated.whitefish.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Ate donated whitefish fillets') %>%
  kable_styling(full_width=FALSE, latex_options=c("HOLD_position"))
```

Q29. Do you or your family ever eat fish **caught** from Flathead Lake either by you, a family member, or a friend of the family?
```{r Caught, echo=FALSE}
knitr::kable(Caught.fish.out,
       booktabs = TRUE,
       col.names = c("","n","%", "n", "%"), 
       align = c('l', rep('c', 4)),
       caption = 'Ate locally caught fish') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position")) %>%
  add_header_above(c(" " = 1, "2021 study"= 2, "2008 study"= 2))
```
\newpage
Q30. When you or your family eat fish **caught** from Flathead Lake, which types of fish do you eat? Do you eat lake trout?
```{r Caught LT, echo=FALSE}
knitr::kable(Caught.lake.trout.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Ate locally caught lake trout') %>%
  kable_styling(full_width=FALSE, latex_options=c("HOLD_position"))
```

Q31. Do you eat lake whitefish?
```{r Caught WF, echo=FALSE}
knitr::kable(Caught.whitefish.out,
       booktabs = TRUE,
       col.names = c("","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Ate locally caught whitefish') %>%
  kable_styling(full_width=FALSE, latex_options=c("HOLD_position"))

```

Q32. When you or your family eat fish **caught** from Flathead Lake, are they generally small (less than 14 inches), medium (between 14 and 26 inches), or large (over 26 inches)?
```{r CaughtSize, echo=FALSE}
knitr::kable(Catch.Size.out,
       booktabs = TRUE,
       col.names = c("Size","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Size of locally caught fish') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))

```
## Knowledge of Mercury Contamination in Fish & Consumption Advisory
This next set of questions are about mercury contamination in fish and fish consumption advisories

Q34. How much do you know about mercury contaminants in fish? Would you say you know a lot, some, very little or nothing at all?
```{r HgKknowledge, echo=FALSE}
knitr::kable(HgKnow.out,
       booktabs = TRUE,
       col.names = c("","n","%", "n", "%"), 
       align = c('l', rep('c', 4)),
       caption = 'Knowledge of mercury contamination in fish') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position")) %>%
  add_header_above(c(" " = 1, "2021 study"= 2, "2008 study"= 2))
```
\newpage
Q35. Some states and tribes issue consumption advice for fish contaminated with mercury.  Are you aware of CSKT's advisory on eating locally caught fish?
```{r CSKT HgKknowledge, echo=FALSE}
knitr::kable(Advisory.out,
       booktabs = TRUE,
       col.names = c("","n","%", "n", "%"), 
       align = c('l', rep('c', 4)),
       caption = 'Knowledge of CSKTs fish consumption advisory') %>%
  kable_styling(full_width=FALSE, latex_options=c("HOLD_position")) %>%
  add_header_above(c(" " = 1, "2021 study"= 2, "2008 study"= 2))
```
*The following questions were asked of respondents who said they were aware of CSKT's fish advisory*

Q36. Where did you learn about CSKT's fish advisory? (check all that apply)
```{r Source, echo=FALSE}
knitr::kable(Advisory.source,
       booktabs = TRUE,
       col.names = c("Source","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Source for learning about CSKT fish advisory') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```

Q38. How much would you say you know about the following parts of the fish consumption guidelines. The fish species included in the advisory?  Would you say you know a lot, some, very little or nothing at at all?
```{r Species HgKknowledge, echo=FALSE}
knitr::kable(Species.out,
       booktabs = TRUE,
       col.names = c("","n","%", "n", "%"), 
       align = c('l', rep('c', 4)),
       caption = 'Knowledge of species included in the advisory') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position")) %>%
  add_header_above(c(" " = 1, "2021 study"= 2, "2008 study"= 2))
```
\newpage
Q39. The size of the fish that should be avoided?  Would you say you know a lot, some, very little or nothing at all?
```{r Size HgKknowledge, echo=FALSE}
knitr::kable(Size.out,
       booktabs = TRUE,
       col.names = c("","n","%", "n", "%"), 
       align = c('l', rep('c', 4)),
       caption = 'Knowledge of size of fish to be avoided') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position")) %>%
  add_header_above(c(" " = 1, "2021 study"= 2, "2008 study"= 2))
```

Q40. The amount of fish that can be safely eaten? Would you say you know a lot, some, very little or nothing at all?
```{r Quantity HgKknowledge, echo=FALSE}
knitr::kable(Quantity.out,
       booktabs = TRUE,
       col.names = c("","n","%", "n", "%"), 
       align = c('l', rep('c', 4)),
       caption = 'Knowledge of the amount of fish that can be eaten safely') %>%
  kable_styling(full_width=FALSE, latex_options=c("HOLD_position")) %>%
  add_header_above(c(" " = 1, "2021 study"= 2, "2008 study"= 2))
```
## Demographics
This is the last set of questions I have for you today.

Q42. How often did you visit this food pantry over the last year?  Did you visit every month, every other month, once every 3 months or infrequently?
```{r Visits, echo=FALSE}
knitr::kable(Visits.out,
       booktabs = TRUE,
       col.names = c("Size","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Frequency of food pantry use') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```
\newpage
Q43. What is your age?
```{r Age, echo=FALSE}
knitr::kable(Age.out,
       booktabs = TRUE,
       col.names = c("Size","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Age distribution') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```

Q44. What is your relationship status?  Are you singel, married, member of an unmarried couple, divorced or separated?
```{r Relationship, echo=FALSE}
knitr::kable(Relationship.out,
       booktabs = TRUE,
       col.names = c("Size","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Relationship status') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))
```

Q45. What is the highest level of education that you've completed?
```{r Education, echo=FALSE}
knitr::kable(Education.out,
       booktabs = TRUE,
       col.names = c("Size","n","%"), 
       align = c('l', rep('c', 4)),
       caption = 'Educational level completed') %>%
  kable_styling(full_width=FALSE, latex_options=c("hold_position"))

```




